Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2019-12-27 analysis/paper/paper.Rmd
changed name of chunk for extrapolation r2 table

```{r extrap-table}
mod_fit_df = model_svy_df %>%
  select(response, data) %>%
  unnest(cols = data) %>%
  select(response, obs = qrf_cap) %>%
  group_by(response) %>%
  mutate(id = 1:n()) %>%
  left_join(model_svy_df %>%
              mutate(pred_full = map(mod_full,
                                     .f = function(x) {
                                       predict(x,
                                               type = 'response') %>%
                                         as_tibble() %>%
                                         rename(pred_full = response,
                                                pred_full_se = SE)
                                     }),
                     pred_no_champ = map(mod_no_champ,
                                         .f = function(x) {
                                           predict(x,
                                                   type = 'response') %>%
                                             as_tibble() %>%
                                             rename(pred_no_champ = response,
                                                    pred_no_champ_se = SE)
                                         })) %>%
              select(response, starts_with("pred")) %>%
              unnest(cols = starts_with("pred")) %>%
              group_by(response) %>%
              mutate(id = 1:n())) %>%
  ungroup()

>>>>

```{r extrap-r2-table}
mod_fit_df = model_svy_df %>%
  select(response, data) %>%
  unnest(cols = data) %>%
  select(response, obs = qrf_cap) %>%
  group_by(response) %>%
  mutate(id = 1:n()) %>%
  left_join(model_svy_df %>%
              mutate(pred_full = map(mod_full,
                                     .f = function(x) {
                                       predict(x,
                                               type = 'response') %>%
                                         as_tibble() %>%
                                         rename(pred_full = response,
                                                pred_full_se = SE)
                                     }),
                     pred_no_champ = map(mod_no_champ,
                                         .f = function(x) {
                                           predict(x,
                                                   type = 'response') %>%
                                             as_tibble() %>%
                                             rename(pred_no_champ = response,
                                                    pred_no_champ_se = SE)
                                         })) %>%
              select(response, starts_with("pred")) %>%
              unnest(cols = starts_with("pred")) %>%
              group_by(response) %>%
              mutate(id = 1:n())) %>%
  ungroup()
